---
title: "HW 5 - Legos"
author: "Annie Hou"
date: "02/26/2024"
output: html_document
---

## Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse)
```

```{r load-rda}
load("data/lego_sales.rda")
```

## Exercises

### Exercise 1

In this sample, the three most common names of purchasers are Jackson, Jacob, and Joseph.

```{r ex1}
common_first_names <- lego_sales %>%
  group_by(first_name) %>%
  summarise(count = n()) %>%
  arrange(desc(count))

print(common_first_names)
```


### Exercise 2

In this sample, the three most common themes of Lego sets purchased are Star Wars, Nexo Knights, and Gear (tied with Mixels).

```{r ex2}
common_themes <- lego_sales %>%
  group_by(theme) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) 

print(common_themes)
```


### Exercise 3

Among the most common theme of Lego sets purchased (which is Star Wars from the previous exercise), the most common subtheme is Skybound; but there are more subthemes not available, so we could better determine the most common purchased subtheme is the data is more complete.

```{r ex3}
most_common_theme <- lego_sales %>%
  mutate(theme = "Star Wars") %>%
  count(subtheme) %>%
  arrange(desc(n))

print(most_common_theme)
```


### Exercise 4

...

### Exercise 5

...

### Exercise 6

...

### Exercise 7

...

### Exercise 8

...

### Exercise 9

...
