---
title: "HW 5 - Legos"
author: "Annie Hou"
date: "02/26/2024"
output: html_document
---

## Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse)
```

```{r load-rda}
load("data/lego_sales.rda")
```

## Exercises

### Exercise 1

In this sample, the three most common names of purchasers are Jackson, Jacob, and Joseph.

```{r ex1}
common_first_names <- lego_sales %>%
  group_by(first_name) %>%
  summarise(count = n()) %>%
  arrange(desc(count))

print(common_first_names)
```


### Exercise 2

In this sample, the three most common themes of Lego sets purchased are Star Wars, Nexo Knights, and Gear (tied with Mixels).

```{r ex2}
common_themes <- lego_sales %>%
  group_by(theme) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) 

print(common_themes)
```


### Exercise 3

Among the most common theme of Lego sets purchased (which is Star Wars from the previous exercise), the most common subtheme is Skybound; but there are more subthemes not available, so we could better determine the most common purchased subtheme is the data is more complete.

```{r ex3}
most_common_theme <- lego_sales %>%
  mutate(theme = "Star Wars") %>%
  count(subtheme) %>%
  arrange(desc(n))

print(most_common_theme)
```


### Exercise 4

```{r ex4}
lego_sales <- lego_sales %>%
  mutate(age_group = case_when(
    age <= 18 ~ "18 and under",
    age >= 19 & age <= 25 ~ "19 - 25",
    age >= 26 & age <= 35 ~ "26 - 35",
    age >= 36 & age <= 50 ~ "36 - 50",
    age >= 51 ~ "51 and over"
  ))

print(lego_sales)

```


### Exercise 5

The age group between 36-50 has purchased the highest number of Lego sets.

```{r ex5}
top_age_quantity <- lego_sales %>%
  group_by(age_group) %>%
  summarise(total_quantity = sum(quantity, na.rm = TRUE)) %>%
  arrange(desc(total_quantity)) 

print(top_age_quantity)
```


### Exercise 6

The age group between 36-50 has spent the most money on Legos.

```{r ex6}
top_age_spending <- lego_sales %>%
  mutate(total_spent = quantity * us_price) %>%
  group_by(age_group) %>%
  summarise(total_spending = sum(total_spent, na.rm = TRUE)) %>%
  arrange(desc(total_spending)) 

print(top_age_spending)
```


### Exercise 7

The theme Star Wars has made the most money for Lego.

```{r ex7}
theme_revenue <- lego_sales %>%
  mutate(revenue = quantity * us_price) %>%
  group_by(theme) %>%
  summarise(total_revenue = sum(revenue, na.rm = TRUE)) %>%
  arrange(desc(total_revenue)) 

print(theme_revenue)
```


### Exercise 8

The phone number area code that has spent the most money on Legos is 956. This area code is located in the Lower and Middle Rio Grande Valley regions in Texas, which includes the communities of Brownsville, McAllen, Laredo and South Padre Island.

```{r ex8}
area_code_spending <- lego_sales %>%
  mutate(
    area_code = str_extract(phone_number, "\\d{3}"),
    revenue = quantity * us_price) %>%
  group_by(area_code) %>%
  summarise(total_revenue = sum(revenue, na.rm = TRUE)) %>%
  arrange(desc(total_revenue)) 

print(area_code_spending)

```


### Exercise 9

The question I wanted to ask is "how does the quantity of Lego sets purchased correlate with their piece count and price?"

From the plot, it is pretty reasonable that the price tends to increase if the piece count increases as the points show a positive correlation. Also, the points are more clustered towards the lower end of the piece count and price axes (left-bottom corner) and with darker color, which means that Lego sets with fewer pieces and lower prices are purchased more frequently. This trend suggests that less complex sets are generally more popular, probably because they are more affordable. There are very less "outliers" which has very high piece count and high price, and they are less purchased. But it also shows the diversity of the Lego product and the variances in consumer preferences during purchasing.

```{r ex9}
ggplot(lego_sales, aes(x = pieces, y = us_price, color= quantity)) +
  geom_point(alpha = 0.4) + 
  scale_size_continuous(range = c(1, 10)) + 
  labs(x = "Piece Count", y = "Price (USD)", color = "Quantity Purchased") +
  theme_minimal() +
  ggtitle("Correlation of Lego Set Piece Count and Price with Quantity")

```

